Class 2: The Quest for Causality

### 2019-09-03 content/class/01-class.Rmd
Fix treatments in slides
Add class 3 content

---
title: "Class 1: Introduction to Econometrics"
citeproc: false
bibliography: ../../static/bib/references.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    template: ../../pandoc/toc-title_html.template
    toc: true
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "1.1 Introduction to Econometrics - Class Notes"
citeproc: false
bibliography: ../../static/bib/references.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    template: ../../pandoc/toc-title_html.template
    toc: true
editor_options: 
  chunk_output_type: console
---

*Tuesday, August 27, 2019*

@@

Please use your hood email address and real name.

### 2019-09-03 content/class/02-class.Rmd
Add reminder to do survey to class 2
Add class 3 content

---
title: "Class 1: Introduction to Econometrics"
citeproc: false
bibliography: ../../static/bib/references.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    template: ../../pandoc/toc-title_html.template
    toc: true
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Class 2: The Quest for Causality"
citeproc: false
bibliography: ../../static/bib/references.bib
csl: ../../static/bib/chicago-syllabus-no-bib.csl
output:
  blogdown::html_page:
    template: ../../pandoc/toc-title_html.template
    toc: true
editor_options: 
  chunk_output_type: console
---

*Thursday, August 29, 2019*

@@

# Statistics Survey

Don't forget to do the [preliminary survey](/assignment/00-preliminary-survey.html) for next class!
